Report on a Safety Checker for Petri nets

### 2014-01-30 paper/workspace/main.tex
Added pseudocode for method safety

@@

  Input:
    (S, T, E, M0) : Petri net
  Output:
    C : State constraints

>>>>

  - Negated Property \neg P:

    cs1 + cs2  >= 2

@@

  Input:
    (S, T, E, M0) : Petri net
  Output:
    C : State constraints
  Pseudocode:

  # Place equations
  for s in S:
    # initial number of tokens
    print(s + " = " + M0(s)"
    for t in T:
      if (t, s) in E and not (s, t) in E:
        # input transition
        print(" + " t)
      if (s, t) in E and not (t, s) in E:
        # output transition
        print(" - " t)
    print("\n")

  # Non-negativity conditions
  for s in S:
    print(s + " >= 0\n")
  for t in T:
    print(t + " >= 0\n")
\end{verbatim}
